Paper Title*

### 2018-12-25 paper.tex
lorawan definition

\par Lowest SF suitable area section is relatively higher then the others. Most of the end devices which close to GW will fall into this area. Figure~\ref{fig:problem1}

\par End devices near the GW will probably select lowest SF all the time. Which results a lot of collisions between lowest SF transmissions while end device number near the GW increases. Figure~\ref{fig:problem2}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{lora0}
\caption{Different SF transmission ranges.}
\label{fig:problem1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{lora1}
\caption{Collision between nodes close to the GW.}
\label{fig:problem2}
\end{figure}

@@

\section{Proposed Technique} \label{Proposed Technique}
\par If GW force some of close end nodes to select higher SF even if they can able to communicate with lower SF, this will result lower collisions due to the orthogonality of different SF. Figure~\ref{fig:proposal_single_gw}

\par GW can avoid increasing SF of end nodes which is close to other GW using location information obtained by triangulating the signal strength of end nodes. Figure~\ref{fig:proposal_multi_gw}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{lora2}
\caption{Collision between nodes close to the GW can be prevented by using higher SF.}
\label{fig:proposal_single_gw}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{lora3}
\caption{Collision prevention proposal for intersecting GWs.}
\label{fig:proposal_multi_gw}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{sf_1000}
\caption{PDR of different SF when radius is 1000m.}
\label{fig:sf_1000}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{sf_3000}
\caption{PDR of different SF when radius is 3000m.}
\label{fig:sf_3000}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{sf_10000}
\caption{PDR of different SF when radius is 10000m.}
\label{fig:sf_10000}
\end{figure}

>>>>

\par Lowest SF suitable area section is relatively higher then the others. Most of the end devices which close to GW will fall into this area.

\par End devices near the GW will probably select lowest SF all the time. Which results a lot of collisions between lowest SF transmissions while end device number near the GW increases. Figure~\ref{fig:collision}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{collision}
\caption{Collision between nodes near the GW.}
\label{fig:collision}
\end{figure}

@@

\section{Proposed Technique} \label{Proposed Technique}
\par If GW force some of close end nodes to select higher SF even if they can able to communicate with lower SF, this will result lower collisions due to the orthogonality of different SF. Figure~\ref{fig:collision_solution_single_gw}

\par GW can avoid increasing SF of end nodes which is close to other GW using location information obtained by triangulating the signal strength of end nodes. Figure~\ref{fig:collision_solution_multi_gw}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{collision_solution_single_gw}
\caption{Collision between nodes close to the GW can be prevented by using higher SF.}
\label{fig:collision_solution_single_gw}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{collision_solution_multi_gw}
\caption{Collision prevention proposal for intersecting GWs.}
\label{fig:collision_solution_multi_gw}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{sf_pdr}
\caption{PDR of different spreading factors.}
\label{fig:sf_1000}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{gw_pdr}
\caption{PDR of different gateway numbers.}
\label{fig:sf_3000}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{r_pdr}
\caption{PDR of different topology radius.}
\label{fig:sf_10000}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{pr_pdr}
\caption{PDR of different packet rates.}
\label{fig:sf_10000}
\end{figure}
